\chapter*{Acknowledgments}

I would like to express my deepest gratitude to my academic supervisor Prof. Pawel Herman at the school of Computer Science and Communication at the Royal Institute of Technology (KTH), for the helpful feedback and continuous support through the research and writing of this thesis. He consistently allowed this thesis to be my own work, but guided me in the right direction whenever I needed. 
I wish to express a sincere thank to my industrial supervisor at King.com, Stefan Freyr Gudmundsson, for his continuous support, advice and discussions throughout the journey of this research. His guidance and extensive knowledge helped me in all the time of writing and research of this thesis.
I would like to thank my external academic supervisor, Prof. Pier Luca Lanzi at the Department of Electronics, Information and Bioengineering (DEIB) at the Politecnico of Milan (Polimi), for the help and support through the writing of this thesis. 
I want to thank my examiner, Prof. Sarunas Girdzijauskas at the school of Information and Communication Technology at KTH, who accepted to take this role. 

Furthermore, I want to thank my colleagues in the Artificial Intelligence team at King, Marcus Adamsson, Rachael Ann, Philipp Eisen, Erik Poromaa, Alex Nodet, Sami Purmonen, Vivek Grimm, Christian Schmidli and Lele Cao for their support that helped me to overcome the obstacles I encountered in this research. Especially, I want to say a particular "thank you" to Philipp Eisen who set the foundations for this research and to Marcus Adamsson for all the fun we have had in the period of this thesis.
Moreover, I would like to thank Bartlomiej Kozakowski, for the help with statistical analysis and the interesting feedback on my research.

Finally, I want to express my very profound gratitude to my family that helped me reaching this milestone of my life and I want to direct a special "thank you" to my girlfriend Daiana Concilio, for the motivation, patience and continuous encouragement throughout my years of study and the process of writing of this thesis. This accomplishment would not have been possible without them.


\vspace{1.0cm}

\noindent
Stockholm, \today

\noindent
\textit{Davide Anghileri}